\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-28 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}. A sensitivity study of capillary forces and viscosity ratios were conducted to assess the impact on fingers' formation, branchiness and dimensions. 
the impact of fluids' interfacial tension on formation and growth of fingers in Hele-Shaw Cells. Their calculations were based on \citet{mclean_1981} semi-analytical solution that correlate

>>>>

Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}. A sensitivity study was conducted to assess the impact on fingers' formation, dimensions and branchiness for a range of viscosity ratios $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary numbers $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U\mu\gamma^{-1}(W/b)^{2}$, where $U$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$. Finger width

%and viscosity ratios 10$^{2}\le${\it VR}$\le$10$^{4}$ and 632$\leN_{C}^{'}\le$6.32$\times$10$^{7}$. 
%the impact of fluids' interfacial tension on formation and growth of fingers in Hele-Shaw Cells. Their calculations were based on \citet{mclean_1981} semi-analytical solution that correlate
